---
title: "Homework 1"
author: Matthew Angulo
output: github_document
---

This is my solution to HW1

```{r}
library(tidyverse)
```


## Problem 1

Create a data frame with the specified elements.

```{r create_df}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low","low","low","med", "med", "med", "med", "high", "high", "high"))
  )

prob1_df
```

Take the mean of each variable in my data frame

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character or factor. 

Now converting variables to numeric.

```{r try_numeric, results= "hide"}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))

```

Character variables cannot be converted to numeric.


Now, converting the logical variable into numeric or factor and then multiplying it by the random sample 

```{r convert_logical}
as.numeric(pull(prob1_df, samp_gt_0))*pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0))*pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0)))*pull(prob1_df, samp)
```

Factors of logical variables cannot be multiplied by numbers  


## Problem 2

```{r}
data("penguins", package = "palmerpenguins")
penguins
```
 
 The Penguins dataset is a summary of information on penguins.  The dataset has `r nrow(penguins)` variables and `r ncol(penguins)` observations. The included variables are: `r names(penguins)`.
 
 The mean flipper length (rounded to the nearest mm) of penguins with nonmissing values in this dataset is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE))` mm
 
Below is a scatterplot comparing flipper length to bill length, color coated by species. 

```{r scatterplot}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species))+geom_point()

ggsave(
  "p8105_hw1_ma3997.pdf")
```
 
 

 
 